Hourly Assimilation of Different Sources of Observations Including Satellite Radiances in a  Mesoscale Convective System Case During RELAMPAGO campaign

### 2022-07-29 analysis/paper/paper_ana_20181122.Rmd
Boundary conditions

We use a 60-member ensemble where the ensemble mean at the beginning of the DA cycle is initialized using the GFS deterministic analysis with random perturbations to generate the initial ensemble perturbations. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5$^{\circ}$ horizontal grid spacing with a smooth time evolution as in @necker2020 and @maldonado2021. In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. This method helps to prevent an underestimation of the ensemble spread [@ouaraini2015], and the random perturbations are also applied at the boundaries to maintain proper levels of ensemble spread within the domain.

@@

Comparing the specific humidity in the experiments (Figures \@ref(fig:TQ-diff)d-f), the impact of assimilating AWS with fine spatial and temporal resolution is most substantial at low levels (Figure \@ref(fig:TQ-diff)d). The PBL in the AWS experiment is consistently moister than in the CONV experiment particularly at nighttime. The increase in low-level moisture by a denser surface network is consistent with previously reported dry biases in the WRF model over the region [@ruiz2010]. We found that the moistening of the PBL is mainly driven by the covariance between temperature and specific humidity within the PBL. In our experiment and over the center of the domain, this covariance remains negative, increasing low-level moisture as the observations introduce negative temperature corrections. As for the temperature, the systematic impact of satellite-derived winds on moisture is small (Figure \@ref(fig:TQ-diff)e). Figure \@ref(fig:TQ-diff)f shows that radiances reduce low-middle level moisture during the first day of the experiment. The drying effect extends to lower-middle levels during the second day of the experiment coinciding with the development of the MCS between 00 and 12 UTC Nov 22.

@@

To quantify the spatial match between the observed precipitation and the first-guess hourly accumulated precipitation for the different experiments, we compute the FSS in 6-hour moving windows for different thresholds and spatial scales (Figure \@ref(fig:fss)). All experiments show similar values of FSS during the initiation of the convection before 06 UTC Nov 22 except for RAD which performs better than the rest of the experiments during this period. This indicates that radiance observations have a positive impact on the analysis. The FSS for CONV is the lowest compared to the rest of the experiments and the differences are larger during the mature stage of the MCS. AWS and SATWND show similar FSSs indicating that satellite-derived wind assimilation has little impact on the precipitation for this case study. The assimilation of radiances led to an overall improvement of the 1-hour forecast precipitation, particularly for the 25 mm threshold during the period of heaviest precipitation on Nov 22 (Figure \@ref(fig:fss)b,d). The enhancement is also important at the developing stage of the MCS (between 00 and 12 UTC Nov, 22 and also for spatial scales above 500 km, not shown).

@@

In this section, we analyze the 60-member ensemble forecast initialized at 00 and 06 UTC Nov 22 from each experiment that runs for 36 and 30 h respectively, until 12 UTC Nov 23. We calculated the FSS for the ensemble forecasts in 6-hour moving windows for the same thresholds and spatial scales as for the first-guess hourly accumulated precipitation to quantify the skill of the forecasts to predict precipitation (Figure \@ref(fig:fssfcst)). CONV forecasts perform very poorly in terms of the FSS compared with the experiments that include other sources of observations. AWS, SATWND, and RAD show improvements in the FSS values, particularly for the higher threshold (Figure \@ref(fig:fssfcst)b, d). Moreover, the late initialization at 06 UTC performs better for AWS, SATWND, and RAD than the forecast initialized at 00 UTC, highlighting the positive impact of the observations assimilated between 00 and 06 UTC.

>>>>

We use a 60-member ensemble where the ensemble mean at the beginning of the DA cycle is initialized using the GFS deterministic analysis with random perturbations to generate the initial ensemble perturbations. The perturbations are generated as scaled differences between two random atmospheric states obtained from the Climate Forecast System Reanalysis (CFSR) data with 0.5$^{\circ}$ horizontal grid spacing with a smooth time evolution as in @necker2020 and @maldonado2021. In this way, we preserved the nearly hydrostatic and geostrophic equilibrium of larger scales. This method helps to prevent an underestimation of the ensemble spread [@ouaraini2015]. All experiments presented here uses the same boundary conditions from GFS, generated using the same method as for the inicial conditions to maintain proper levels of ensemble spread within the domain.

@@

Comparing the specific humidity in the experiments (Figures \@ref(fig:TQ-diff)d-f), the impact of assimilating AWS with fine spatial and temporal resolution is most substantial at low levels (Figure \@ref(fig:TQ-diff)d). The PBL in the AWS experiment is consistently moister than in the CONV experiment particularly at nighttime. The increase in low-level moisture by a denser surface network is consistent with previously reported dry biases in the WRF model over the region [@casaretto2022, @matsudo2021, @ruiz2010]. We found that the moistening of the PBL is mainly driven by the covariance between temperature and specific humidity within the PBL. In our experiment and over the center of the domain, this covariance remains negative, increasing low-level moisture as the observations introduce negative temperature corrections. As for the temperature, the systematic impact of satellite-derived winds on moisture is small (Figure \@ref(fig:TQ-diff)e). Figure \@ref(fig:TQ-diff)f shows that radiances reduce low-middle level moisture during the first day of the experiment. The drying effect extends to lower-middle levels during the second day of the experiment coinciding with the development of the MCS between 00 and 12 UTC Nov 22.

@@

We computed the FSS to quantify the spatial match between the observed precipitation and the first-guess hourly accumulated precipitation for the different experiments (Figure \@ref(fig:fss)). For each threshold and spatial scale, we applied Equation \@red(eq:eq7) in 6-hours rolling windows throughout the experiment period. All experiments show similar values of FSS during the initiation of the convection before 06 UTC Nov 22 except for RAD which performs better than the rest of the experiments during this period. This indicates that radiance observations have a positive impact on the analysis. The FSS for CONV is the lowest compared to the rest of the experiments and the differences are larger during the mature stage of the MCS. AWS and SATWND show similar FSSs indicating that satellite-derived wind assimilation has little impact on the precipitation for this case study. The assimilation of radiances led to an overall improvement of the 1-hour forecast precipitation, particularly for the 25 mm threshold during the period of heaviest precipitation on Nov 22 (Figure \@ref(fig:fss)b,d). The enhancement is also important at the developing stage of the MCS (between 00 and 12 UTC Nov, 22 and also for spatial scales above 500 km, not shown).

@@

In this section, we analyze the 60-member ensemble forecast initialized at 00 and 06 UTC Nov 22 from each experiment that runs for 36 and 30 h respectively, until 12 UTC Nov 23. We calculated the FSS for the ensemble forecasts in 6-hour rollig windows for the same thresholds and spatial scales as for the first-guess hourly accumulated precipitation to quantify the skill of the forecasts to predict precipitation (Figure \@ref(fig:fssfcst)). CONV forecasts perform very poorly in terms of the FSS compared with the experiments that include other sources of observations. AWS, SATWND, and RAD show improvements in the FSS values, particularly for the higher threshold (Figure \@ref(fig:fssfcst)b, d). Moreover, the late initialization at 06 UTC performs better for AWS, SATWND, and RAD than the forecast initialized at 00 UTC, highlighting the positive impact of the observations assimilated between 00 and 06 UTC.
